
% a4 size:  8.27 × 11.69 in
% letter size: 8.5 x 11 in

\documentclass[a4paper,11pt]{article}
%\documentclass[letterpaper,12pt]{article}

\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

%Margin setup
\setlength{\paperwidth}{8.27in}
\setlength{\paperheight}{11.69in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{10.69in}
\setlength{\topmargin}{-0.5in}
\setlength{\textwidth}{7.27in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.5in}
\setlength{\evensidemargin}{-0.5in}

% no headers and footers
\pagestyle{empty}
% don't add extra spaces
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}
    {\vspace{-4pt}\scshape\raggedright\large} %format
    {} %label
    {0pt} % sep
    {} % before code
    [\titlerule \vspace{-5pt}] % after code

% Custom commands
\newcommand{\work}[4]{
    \begin{tabular*}{7.1in}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\degree}[4] {
    \listitemone
	\begin{tabular*}{7.1in}{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\liststart}{\begin{itemize}[leftmargin=10pt]}
\newcommand{\listend}{\end{itemize}}
\newcommand{\listitemone}{\item}
\newcommand{\listitemtwo}{\item[$\circ$]}

\newcommand{\skill}[2] {
    \textbf{#1} #2 \\
    \vspace {3pt}
}

\newcommand{\project}[2] {
    \listitemone
    \textbf{#1} #2
    \vspace{1pt}
}

\newcommand{\cert}[2] {
    \listitemone
	\begin{tabular*}{7.1in}{l@{\extracolsep{\fill}}r}
	    {#1} & \textit{#2}
	\end{tabular*}\vspace{-6pt}
}


\begin{document}
% Heading
\begin{center}
    \textbf{\Large MUHAMMAD YASIR KHAN}
\end{center}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \href{https://www.linkedin.com/in/mykhani}{https://www.linkedin.com/in/mykhani}&
    
    Email: \href{mailto: yasir_electronics@yahoo.com}
                {yasir\_electronics@yahoo.com}\\
	
	\href{https://www.github.com/mykhani}
	     {https://www.github.com/mykhani}&
	
	Contact: +852-66106227, Hong Kong
\end{tabular*}


\vspace{0.1in}
% Education
\section{Education}
\begin{itemize}[leftmargin=*]
    \degree {National University of Sciences \& Technology}
            {Islamabad, Pakistan}{BE. Electronics Engineering}{Oct. 2008 - Aug. 2012}
        \begin{itemize}[leftmargin=0.2in]
            \listitemtwo
                Relevant courses: Embedded Systems, Computer Networks, Digital and Analog Electronics, Power Electronics, FPGA based design, Computer Architecture, Fundamentals of Programming, Operating Systems, Digital Signal Processing, Calculus, Linear Algebra, Numerical Analysis
        \end{itemize}
\end{itemize}
\vspace*{-\baselineskip}


\vspace{0.005in}
% Skills
\section{Skills}
\skill{Languages:} {C, C++ (17), JavaScript (ES6), Python, ARM assembly}

\skill{Software:} {Microcontrollers, Linux (system programming, application development, device drivers, porting, board support, Yocto), RTOS (FreeRTOS), GUI applications using Qt5, Git, Object Oriented Programming, Datastructures \& Algorithms, Web applications}

\skill{Hardware:} {PCB design and development, Electronic circuit design,               use of electronic tools (digital logic analyzer, oscilloscope),
                   electronic prototyping, reading
                   datasheets, manuals and schematics}

\skill{Processors/Platforms:} {ARM Cortex M4, STM32, ESP8266, Beaglebone Black, RaspberryPi}

\skill{SDK/Frameworks:} {Yocto Project, Qt5, STM32CubeIDE, ROS, React, Redux, NodeJS}

\skill{Communication protocols} {Sockets programming, AJAX, REST API, UART, I2C, SPI, USB}

\skill{Tools:} {Kicad (PCB design), Linux command-line tools for 	  	 		            compilation, make, cmake}

\skill{Documentation} {Writing technical documents, user guides, reviews}


\vspace{0.005in}
% Certifications
\vspace{0.005in}
\section{Certifications}
\liststart
    \cert{Embedded Linux kernel \& driver development}{Mentor Graphics}
    \cert{\href{https://www.udemy.com/certificate/UC-014143dc-66f6-4203-addc-3c255e54ddbb/}{Embedded Systems Programming on ARM Cortex-M3/M4}}	  	          {Udemy}
    \cert{\href{https://www.udemy.com/certificate/UC-39a37dc0-8a26-4721-a7f4-61e2600e380e}{ARM Assembly Language from Ground Up}}	  	          {Udemy}
    \cert{\href{https://www.udemy.com/certificate/UC-VRNTEUJM/}{Advanced C++ programming}}{Udemy}
    \cert{\href{https://www.udemy.com/certificate/UC-0RLGR3RM/}{Modern C++ 		  concurrency in depth}}{Udemy}
    \cert{\href{https://www.udemy.com/certificate/UC-088f030e-b644-42e5-b2ee-a1cd61a53e96/}{Design Patterns in Modern C++}}{Udemy}
    \cert{\href{https://www.udemy.com/certificate/UC-A7SUDAR3/}				          {Introduction to RTOS}}{Udemy}
    \cert{\href{https://www.udemy.com/certificate/UC-b6b01a07-f2f0-4e2f-add1-37981acecf1f/}{The Complete JavaScript Course 2021}}{Udemy}
    \cert{\href{https://www.udemy.com/certificate/UC-11f326fc-276b-4cee-b3bf-1cb8c1529cc1/}{2021 Complete Python Bootcamp}}{Udemy}
    \cert{\href{https://www.educative.io/verify-certificate/2gKmzmJrwV3t0nlLzJ4pOKfL75574oplqc3}{Web Application \& Software Architecture}}{Educative}
\listend


\vspace{0.005in}
% Experience
\section{Experience}
\liststart
\listitemone
    \work {Nixplay}{Sheung Wan, Hong Kong}
        {Embedded Software Engineer}{Jan. 2019 - present}
	    \begin{itemize}[leftmargin=0.2in]
	        \listitemtwo
	            Developed a multi-threaded firmware for the digital photo frame. Debugged and resolved multimedia (photo, video) related issues. Programmed in C for Allwinner's Melis RTOS platform.
	        \listitemtwo
	            Developed a Yocto based Linux platform with QtWebengine (based on chromium browser) support, as an alternative to the existing Android platform, for our cloud connected devices. Worked with Linux graphics, display and multimedia (GStreamer) frameworks and ported Android kernel changes to the Linux.
	        \listitemtwo
	            Ported the above Linux OS on different embedded boards. Prepared the Linux device tree and kernel configuration. Configured and enabled MIPI LCD displays, GPIO, touch and board-specific drivers.
	        \listitemtwo
	            Developed a test application using Qt5, QML and JavaScript, running on the above platform.
	    \end{itemize}

\listitemone
    \work {The Hong Kong Polytechnic University}{Hung Hom, Hong Kong}
        {Lead Engineer}{Aug. 2017 - Oct. 2018}
	    \begin{itemize}[leftmargin=0.2in]
	        \listitemtwo
	            Developed the hardware and software for an IoT based 
	            hydroponic farming system research project.
	        \listitemtwo
	            Designed and fabricated a small wireless environment sensor board with SMT components.
	        \listitemtwo
	            Developed a nutrient level monitoring and adjustment 
	            system, based on RaspberryPi and off-the-shelf sensors.
	        \listitemtwo
	            Developed the plant imaging system using embedded serial
	            camera and customized lens assembly.
	        \listitemtwo
	            Developed the firmware for LED based grow lights.
	        \listitemtwo
	            Setup a local MQTT server for data collection and 
	            device control.
	        \listitemtwo
	            Modified a commercial wine keeper to grow plants inside it.
	        \listitemtwo
	            Developed a touch based control panel with UI written 
	            in Qt5 to control the wine keeper.
	    \end{itemize}

\listitemone
    \work {Mentor Graphics}{Lahore, Pakistan}
        {Sr. Software Development Engineer}{Nov. 2013 - June 2017}
	    \begin{itemize}[leftmargin=0.2in]
	        \listitemtwo
	            Developed customized Embedded Linux systems using Yocto Project.
	        \listitemtwo
	            Developed Yocto Project based Linux BSPs for  
	            different hardware platforms including iMX6Q and 
	            Xilinx Zynq.
            \listitemtwo
                Debugged and resolved Linux system issues.
            \listitemtwo
                Became proficient in configuring/patching/compiling
                the Linux kernel and writing device drivers.
            \listitemtwo
                Developed the Mentor's multi-core AMP framework for
                booting the Linux and Nucleus RTOS in parallel on
                separate cores of a multi-core ARM processor with a
                shared memory based communication channel and 
                zero-copy transfer.
            \listitemtwo
                Contributed in open source community and successfully
                submitted several patches upstream.
	    \end{itemize}
	    
\listitemone
    \work {East West Infiniti (Pvt) Ltd.}{Islamabad, Pakistan}
        {System Design Engineer}{Oct. 2012 - Oct. 2013}
	    \begin{itemize}[leftmargin=0.2in]
	        \listitemtwo
	            Worked on developing an autonomous air-boat. 
	            Integrated various on-board sensors and wrote the PID
	            based control software for the GPS navigation.
	        \listitemtwo
	            Developed the SONAR based sea tide measurement system.
	        \listitemtwo
	            Added the wireless connectivity to different 
	            products using Wi-Fi, Zigbee and GPRS.
	        \listitemtwo
	            Designed electronic circuits and wrote firmware 
	            for the company's numerous projects. 
	            
	    \end{itemize}
\listend
\vspace*{-\baselineskip}


\vspace{0.005in}
% Projects
\section{Projects}
\liststart

\project{Custom USB device and its Linux driver:}
        {Developed a custom USB device on ARM cortex-M4
         based Texas Instruments TM4C123G microcontroller.     
         TM4C123G USB controller provides USB OTG
         functionality but it was programmed to be in the device mode.
         Wireshark was used to observe USB packets during USB enumeration,
         configuration and data transfer phases. Two endpoints (IN and OUT) were configured on the device side to communicate with the USB host during
         interrupt transfers. Finally, wrote a Linux driver to communicate
         with the device. Link to source: \textbf {http://github.com/mykhani/usbdev} }

\project{STM32RTOS:}
        {My personal project of creating an RTOS from scratch for STM32 series ARM Cortex M4 microcontrollers. See \textbf {https://github.com/mykhani/STM32RTOS} for details and the features implemented so far (priority based scheduling, build system).}

\project{IoT based hydroponic farming:} 
        {Developed a prototype for IoT based 
         hydroponic farming system. Wrote RTOS based firmware
         for the system components; including a custom designed wireless environment sensor, 
         LED grow light brightness and color control, and automatic nutrient monitoring/feeding
         system. Also setup a local mqtt web server to listen in on the field devices and store the transmitted data.}
         
\project{Beaglebone Green Product Review:}
        {Reviewed the BeagleBone Green board for Element14. Explored creating a platform for robotics based development using Beaglebone Green, Robot Operating System (ROS), and the Grove connector system of the Beagleboard Green. The review and some of my other technical blogs can be read at \textbf {https://medium.com/@yasir.gandapur}}
                  
\project{Autonomous air-boat:} 
        {Worked on the development of an air-boat including its mechanical
         assembly and electronics. Integrated electronics
         and sensors and implemented a PID based control software
         for GPS navigation. Conducted extensive experimental testing
         of the boat in a public lake.}
\listend

\end{document}
